Cluster Difference Imaging Photometric Survey. I. Light Curves of Stars in Open Clusters from TESS Sectors 6 \& 7

### 2019-08-10 paper_I/ms.tex
update section 3
Co-authored-by: joshwinn <jwinn@astro.princeton.edu>

\begin{figure*}[!t]
    \begin{center}
        \leavevmode
        \includegraphics[width=0.93\textwidth]{stages_of_image_processing_good.png}
    \end{center}
    \vspace{-0.6cm}
    \caption{
        Stages of image processing for an image taken during the middle
        of an orbit.
        {\it Top right}. Calibrated image.
        {\it Top left}. Smooth background estimate.
        {\it Middle right}. Calibrated image minus its median pixel value.
        {\it Middle left}. Calibrated image minus smooth background.
        {\it Bottom left}. Registered difference image.
        {\it Bottom right}. Zoom of difference image.
        Each image is $(2048\times2048)$ pixels, except for the bottom-right 
        image, which is $(500\times500)$.
        All images except the top-right have the same color map.
        The sector, camera, and CCD are (6, 1, 2).
        \label{fig:stages_good}
    }
\end{figure*}

\begin{figure*}[!t]
    \begin{center}
        \leavevmode
        \includegraphics[width=0.93\textwidth]{stages_of_image_processing_bad.png}
    \end{center}
    \vspace{-0.6cm}
    \caption{
        Same sector, camera and CCD as Figure~\ref{fig:stages_good}, but for an image taken during
        perigee passage, when scattered light from the Earth is
        prominent.
        A number of systematic artifacts are present,
        including vertical ``straps'' and small-scale structure in scattered light
        patches.
        The quality of astrometric registration in the difference image is also
        worse, leading to larger residuals in the lower-right panel.
        \label{fig:stages_bad}
    }
\end{figure*}

@@

To reduce the TESS images to light curves, we adopted a
difference imaging approach.  The overall method is in the spirit of the
reduction pipelines developed by \citet{Pal_2009},
\citet{huang_high-precision_2015}, \citet{soares-furtado_image_2017}
and \citet{oelkers_precision_2018}; a conceptual overview is given in
Figure~\ref{fig:pipeline}.  Most sub-modules of our pipeline have been
developed over the past decade to process HAT data \citep[{\it
e.g.},][]{bakos_hat_review_2018}.  The specific high-level framework
used for this reduction was adapted from a pipeline called
\texttt{pipe-trex}, under development primarily for the HATPI project
(\url{hatpi.org}).  The code is available
online\footnote{\url{github.com/waqasbhatti/pipe-trex}, commit
\texttt{cd9f9bb}.}.

We begin our processing with the calibrated full frame images produced
by the Science Processing Operations Center at NASA Ames
(\S~\ref{subsec:observations}).  We then perform a collection of
preparatory steps, including source extraction of bright stars,
astrometric verification, and coarse simple aperture photometry of
bright stars (\S~\ref{subsec:preparation}).  Using the information
collected from these initial steps, we select an astrometric reference
frame to which we transform all of the calibrated images.  We
construct a photometric reference by stacking a subset of these
transformed frames, after having convolved the frames to have
identical stellar profiles. Finally, we subtract each target frame
from the photometric reference (\S~\ref{subsec:imagesubtraction}).  We
perform aperture photometry on the subtracted images using positions
projected onto the frame from the Gaia-DR2 source catalog.  We detrend
the resulting light curves (\S~\ref{subsec:lcdetrending}).  The
resulting white noise and red noise properties of the light curves,
and a few interesting cases of variability, are discussed in
\S~\ref{sec:results}.

@@

The TESS spacecraft began science operations on July 25, 2018.  To
keep its cameras pointed opposite the Sun, the spacecraft advances by
$\approx$$28$ degrees east in ecliptic longitude every lunar month.
Data acquired throughout each ``sector'' are downlinked at spacecraft
perigee through the Deep Space Network.  Descriptions of the
spacecraft's design and operations are given by
\citet{ricker_transiting_2015} and the instrument handbook
\citep{vanderspek_2018}.

For us, the main data product of interest is the calibrated full frame
image (FFI).  Each TESS camera is read out every 2 seconds.  To
produce a manageable telemetric load, the resulting pixel values are
averaged by the onboard computer into 30 minute exposures. An on-board
cosmic ray mitigation algorithm is applied \citep[][\S
5.1]{vanderspek_2018}. Once transmitted to the ground, the raw images
are calibrated by the Science Processing Operations Center (SPOC).  The
calibration process includes an overscan, bias, and dark current
correction, and also divides out a flat field.  Details are discussed
by \citet{clarke_kepler_2017}, and the resulting science data products
are described by \citet{tess_data_product_description_2018}.

We perform our processing using the calibrated images, their
corresponding uncertainty images, and the associated headers.  The
spacecraft has four cameras, and each camera has four CCDs.  In the
following analysis, all image-level operations are thus performed on
the images for each CCD, so that at any instant of time there are 16
independent images that require analysis.

While we performed numerous initial tests on the first sectors of
data, by geometric coincidence Sectors 1--5 were pointed away from the
galactic plane.  Consequently, less than 2\% of the CDIPS target star
sample was observed in the first five TESS sectors.  Though a few
interesting clusters are present in these observations ({\it e.g.},
Blanco~1, NGC~2516, NGC~1901), for the present work we opted to focus
on sectors in which there were more stars of interest for our intended
science.  These begin in Sector 6 (2018-12-12, spacecraft orbit \#19).
For this run of processing, they conclude at the end of Sector 7
(2019-02-01, spacecraft orbit \#22).
Sectors 6 and 7 cover galactic longitudes from roughly 200$^\circ$ to 280$^\circ$, 
with fair coverage within $\pm 20^\circ$ of the galactic plane
(Figure~\ref{fig:cdips_targets_positions}).

@@

Before we can perform any kind of photometry, a few janitorial tasks
are required.
First, we convert the multi-extension calibrated FITS image from MAST
into a single-extension FITS image, and trim to remove virtual rows
and columns using the \texttt{SCIROWS}, \texttt{SCIROWE},
\texttt{SCCSA}, and \texttt{SCCED} header values.

In order to preemptively address the background variations present in
some frames due to scattered light from the Earth and Moon
\citep[see][\S 7.3.1--7.3.4]{vanderspek_2018}, we then estimate and
subtract the large-scale background.  We do this by temporarily
masking out pixels more than $2\sigma$ from the image median, and then
pass a $48\times48$ median box filter over each pixel in the image,
with reflective boundary conditions.  The resulting background
estimate has low-amplitude structure over spatial scales of a few
pixels, so we then blur it with a gaussian kernel to produce a smooth
background estimate for each image.  These steps also remove a
low-level vignetting present in the corners of many images, which
remains even after flat-fielding \citep[see][\S
7.3.5]{vanderspek_2018}.  
The results are shown in the upper four panels of Figures~\ref{fig:stages_good}
and~\ref{fig:stages_bad}.
Features with spatial scales smaller than $\approx$48 pixels remain, 
but large scale scattered light patches are removed.

@@

After subtracting the background, we mask out saturated pixels using a
fixed saturation level of $8\times10^4\,{\rm ADU}$. This value was
chosen based on the onset of bleeding charge trails in the images, and
is slightly greater than the saturation level of $2\times10^5$
electrons, or about $4\times10^4\,{\rm ADU}$, quoted by
\citet{vanderspek_2018}. 
We correspondingly do not analyze stars brighter than $T\approx 6.5$.
As described by \citet{Pal_2009}, the pixel masks are metadata to the
image, and are only applied to the pixel values during the specific
image processing steps in which they are necessary ({\it e.g.},
convolution). We also extend the masks beyond purely saturated pixels
to ``bloomed'' pixels horizontally and vertically adjacent to the
saturated pixels (see Figure~6 of \citealt{Pal_2009}).

Finally, for frames with the \texttt{DQUALITY} bit-flag corresponding
to the ``momentum dumps'' and ``coarse pointing modes'' described by
\citet{vanderspek_2018}, we omit the entire frame.  This removes on
average a few frames per sector, out of about one thousand. Through
visual inspection, we see that the stars on these frames are extremely
smeared, and are unlikely to produce useful science data.  In
addition, we use the sector-specific data release notes\footnote{\url{
  archive.stsci.edu/tess/tess_drn.html}} to identify further times
with anomalous spacecraft performance, which we omit from
consideration.  For Sectors 6 and 7, this included three days at the
beginning of Sector 6 dedicated to acquiring pixel response function
data, and no additional gaps in Sector 7.
%For Sectors 1 through 5, these
%include coarse pointing windows from orbits 10, 13, 14, and an
%instrumetal anomaly window in orbit 15.
% For Sectors 6 through 8, these include three days at the beginning of
% Sector 6 dedicated to acquiring pixel response function data, and also
% about three days during Sector 8 lost to an instrument anomaly.

@@

First, we perform source extraction on the
thousand or so brightest, non-saturated stars in each image.  
This is done using a \texttt{fitsh} tool, \texttt{fistar}.
We derive centroid positions for the stars, and
simultaneously
fit elongated gaussians to their profiles, yielding the shape
parameters $(s,d,k)$, where the flux $f$ as a function of position
$(x,y)$ in the CCD image plane is assumed to take the form
\begin{align}
  f(x,y) &= B + A \exp \{ -0.5 \times [
    s(\Delta x^2 + \Delta y^2) + \\
    \nonumber
    &d(\Delta x^2 - \Delta y^2) +
    k(2\Delta x \Delta y)
  ]  \},
\end{align}
for $(x_0,y_0)$ the central coordinates of the star,
$\Delta x = x-x_0$, $\Delta y = y - y_0$, $B$ the background
level, and $A$ an arbitrary
flux-scaling constant.
For a nearly circular shape profile, the sharpness $s$ is related to
the FWHM as ${\rm FWHM} \approx 2.35\sqrt{s}$ \citep[{\it
e.g.},][]{Pal_2009}.  These shape parameters are later used when
selecting an astrometric reference frame
(\S~\ref{subsec:imagesubtraction}).  
In agreement with what is obvious upon visual inspection, this 
fitting process shows that stars closer to the
center of each camera's field are round, while
stars near the field edges are more triangular.

For the astrometric solution, we use the World Coordinate System (WCS)
and fourth-order Simple Imaging Polynomial (SIP) coefficients
derived by SPOC and included in the FFI headers
\citep[][Sec.~8]{pence_fits_2010}.  We explored the possibility of
using \texttt{astrometry.net} \citep{lang_2010} to derive our own
astrometric solutions for each frame, but found that the astrometric
residual (the mean separation between projected and measured
positions) was consistently a factor of 1.5-2 times higher in our WCS
solutions than in those given by SPOC.  This was perhaps because
we did not develop a robust
algorithm to select non-blended stars of intermediate brightness before
measuring their positions.
Nonetheless, we did find that extending the astrometric correction
to sixth order (compared to the fourth-order polynomial coefficients
in the SPOC solution) did not improve the quality of the fit.

With the resulting WCS information, we then project a source catalog
onto each frame. 
We use the
projected positions of the sources to center the apertures in our
photometry,
rather than attempting to detect the positions.  Such
``forced-aperture photometry'' is preferable to source
extraction in the crowded fields that are central to this work.  The
Gaia-DR2 epoch is J2015.5, so even the fastest-moving stars with
proper motions of $\sim$$1\,{\rm arcsecond}\,{\rm yr}^{-1}$ are still
well within one pixel of their predicted positions in the TESS images.
The projection from catalog sky-coordinate positions to pixel
coordinates is performed using an analog of the \texttt{wcs-rd2xy}
program that performs the standard matrix algebra \citep{lang_2010}.
The source catalog look-up is performed using
\texttt{gaia2read}\footnote{\url{github.com/samuelyeewl/gaia2read}}
\citep{kim_2018_gaia2read}.

@@

The residual between the measured and projected stellar centroid
positions is displayed for one photometric reference frame in
Figure~\ref{fig:astromresid}.
The construction of this frame will be described shortly, however
a few salient points can first be made.
First, the typical median precision of the WCS solution is a bit below
0.1 pixels, and its $90^{\rm th}$ percentile is typically less than
0.3 pixels\footnote{In fact, in our reduction we automatically impose
that the median residual and 90th percentile remain below 0.2 and 0.4
pixels, respectively.}.
%The distribution has a outlier tail of saturated stars which were
%masked, and thus do not have measureable centroid positions.
The errors are typically largest in the corners of the field of view,
where the non-linearity of the focal plane is most significant, and
the corrections required by the SIP coefficients are largest.
%The final sub-panel of Figure~\ref{fig:astrometricresidual} is a
%sanity check on the location of the projected positions, and also
%gives some context for our chosen aperture radii of 1, 1.5, and 2.25
%pixels.

Finally, to collect the metadata needed
to select photometric reference frames,
we perform
aperture photometry on the
bright stars.
This task is
performed by using \texttt{fiphot} to
sum the counts inside 
circular apertures centered on the projected stellar positions.
The pixel weights are equal to the fraction of the pixel
that falls within the aperture.  They are unity for pixels
entirely within the aperture, and fractional along the aperture
boundary. % (see \citealt{Pal_2009} Fig 17). 
The background levels are measured in annuli around each aperture
center. 
%The raw flux of the object after background removal is then
%(\citealt{Pal_2009} Eq 65)
%\begin{equation}
%  f = \sum_{x,y} w_{x,y} (I_{x,y} - B) = f_{\rm total} - B r_0^2.
%  \label{eq:simple_aperture_phot}
%\end{equation}
The resulting measurements, for instance of the background level of
each aperture, and the number of stars with ``good'' photometry,
can then be used to assess the photometric quality of each frame.

@@

The core operation of ``classical'' image subtraction attempts to
match a photometric reference $R$ and a target image $I$ by computing
and applying a convolution kernel.  For ground-based data, this
``match'' typically corrects for differences in seeing or transparency
between the reference and target; for space-based data, the match
might correct for spacecraft jitter, or thermal and corresponding
point-spread function (PSF) variations.  The kernel, once applied to
the high signal-to noise reference, produces a model image, $M_{xy}$,
\begin{equation}
    M_{xy} = (R \otimes K)_{xy} + B_{xy},
    \label{eq:imagemodel}
\end{equation}
where $B_{xy}$ is a component of the model image that allows for
background variations, and $\otimes$ denotes convolution.  Since we
modeled the background separately (\S~\ref{subsec:preparation}), we
set $B_{xy}=0$.  The convolution kernel $K$ is typically decomposed
onto a basis, $K = \sum_i c_i K_i$, and the coefficients are found by
minimizing
\begin{equation}
    \chi^2 = \sum_{xy} \left( \frac{I_{xy} - M_{xy}}{\sigma_{xy}} \right)^2,
    \label{eq:chisq_conv}
\end{equation}
where $\sigma_{xy}$ is the uncertainty in the target image pixel
values.  Photometry is then performed on the difference image
$D_{xy}$, where $D_{xy} = I_{xy} - M_{xy}$.  For the present
reduction, the uncertainty in each target image pixel was taken to be
a constant.

@@

To make the above high-level picture work, we need to select
two ``reference frames'':
(1) the astrometric reference; and (2) the photometric reference.

To choose the astrometric reference, we search for frames with
large, round stars (big $s$, small $d$ and $k$ values).  We also
require that the frame have minimal background noise, as measured in
annuli around the bright stars selected in
\S~\ref{subsec:preparation}.  Finally, the astrometric reference
needs to have, relative to the other frames being considered, a large
number of detected sources (though the variance between frames was rather 
small).  We sort the frames
using these metrics, and then select the astrometric reference from
successive intersections of each sorted list.

@@

The second required reference frame is the photometric reference,
which is used both to calculate the convolution kernel, and to obtain
a reference flux for each star.  To make it, we first choose 50 images
with low background measurements (measured for each frame from the
annuli around bright stars), and only consider frames with a
relatively large number of detected bright objects.  We then convolve
these candidate photometric reference frames to the frame with the
lowest background measurement, and construct the photometric
reference as the median image across the 50 frame stack.

Measuring the reference flux for each star is a non-trivial
operation.  First, we perform forced simple aperture photometry on the
photometric reference frame to measure the flux for each source.  The
local background is estimated in annuli, with neighboring stars masked
out during the background measurement.  If we were to stop
here, {\it it would be a bad mistake}.  The reference fluxes for faint
stars would be overestimated, due to crowding.  The relative amplitude
of photometric signals for faint stars would correspondingly be biased
small, which would hinder exoplanet detection, among other
applications.

To avoid this problem, after performing simple aperture photometry on
the reference frame, we fitted a line between the catalog $T$-band
magnitude of each star, and its measured flux.  The $T$-band magnitude
was calculated according to Equation~1 of \citet{stassun_TIC8_2019}.
We then use the known catalog magnitude to predict the expected
reference flux for each star.  This minimizes crowding down to Gaia's
resolution limit of $\approx$1$''$, rather than the TESS limit of
$\approx$20$''$.

The final instrumental flux
values $f$ we report are given by \citep[][Equation~83]{Pal_2009} 
\begin{align}
f &=  f_{\rm reference} + f_{\rm subtracted} \\
&=
g \left(T_{\rm cat} \right)
+
\frac{1}{|| K ||_1^2} \sum_{x,y} D_{x,y} (w \otimes K)_{x,y}.
\label{eq:ism_flux_measurement}
\end{align}
The function $g$ takes as input the target star's catalog magnitude
$T_{\rm cat}$, and returns the reference flux.  Its coefficients have
been fit per the procedure just discussed, independently for each
aperture.  The difference image $D$ is equal to $I -  R\otimes K$,
where as in Equation~\ref{eq:imagemodel}, $I$ is the target image
transformed to the astrometric reference, $R$ is the photometric
reference, and $K$ is the convolution kernel.  The weights $w$ from
the circular aperture mask are included in the convolution.  The norm
$|| K ||_1$ is defined by \citet{Pal_2009}~Equation~81.

@@

To solve for the coefficients to the convolution kernel, a
few further assumptions are necessary.  The procedure implemented in
\texttt{ficonv} is to subdivide the image, and within each grid
element find the brightest non-saturated star. These isolated
``stamp'' stars are then used to solve for the coefficients of the
kernel, by minimizing Equation~\ref{eq:chisq_conv} over the sum of all
stamps.  For the kernel basis, we use a linear combination of
delta functions with a flux scaling term
(\citealt{soares-furtado_image_2017} Section 3.3.1 gives the
equations).  In this model, spatial variations of the PSF across the
image are captured by weighting each basis component with spatial
polynomials up to a cut-off order.

>>>>

\begin{figure*}[!t]
    \begin{center}
        \leavevmode
        \includegraphics[width=0.93\textwidth]{stages_of_image_processing_good.png}
    \end{center}
    \vspace{-0.6cm}
    \caption{
        Stages of image processing for an image obtained during the middle
        of an orbit.
        {\it Top right}. Calibrated image.
        {\it Top left}. Smooth background estimate.
        {\it Middle right}. Calibrated image minus its median pixel value.
        {\it Middle left}. Calibrated image minus smooth background.
        {\it Bottom left}. Registered difference image.
        {\it Bottom right}. Zoom of difference image.
        Each image is $(2048\times2048)$ pixels, except for the bottom-right 
        image, which is $(500\times500)$.
        All images except the top-right have the same color map.
        The sector, camera, and CCD are (6, 1, 2).
        \label{fig:stages_good}
    }
\end{figure*}

\begin{figure*}[!t]
    \begin{center}
        \leavevmode
        \includegraphics[width=0.93\textwidth]{stages_of_image_processing_bad.png}
    \end{center}
    \vspace{-0.6cm}
    \caption{
        Same sector, camera and CCD as Figure~\ref{fig:stages_good}, but for an image obtained during
        perigee passage, when scattered light from the Earth is
        prominent.
        A number of systematic artifacts are present,
        including vertical ``straps'' and small-scale structure in scattered light
        patches.
        The quality of astrometric registration in the difference image is also
        worse, leading to larger residuals in the lower-right panel.
        \label{fig:stages_bad}
    }
\end{figure*}

@@

To reduce the TESS images to light curves, we adopted a
difference imaging approach.  The overall method is in the spirit of the
pipelines developed by \citet{Pal_2009},
\citet{huang_high-precision_2015}, \citet{soares-furtado_image_2017}, \citet{oelkers_precision_2018} and \citet{wallace_search_2019}.
Figure~\ref{fig:pipeline} shows a conceptual overview of
our pipeline.  Most modules have been
developed over the past decade to reduce
images taken by the Hungarian Automated Telescope (HAT) network \citep{bakos_hat_review_2018}.  The specific high-level framework
used for this reduction was adapted from a pipeline called
\texttt{pipe-trex}, under development primarily for the HATPI project
(\url{hatpi.org}).  The code is available
online\footnote{\url{github.com/waqasbhatti/pipe-trex}, commit
\texttt{cd9f9bb}.}.

We begin our processing with the calibrated full frame images produced
by the Science Processing Operations Center at NASA Ames
(\S~\ref{subsec:observations}).  We then perform a collection of
preparatory steps, including source extraction of bright stars,
astrometric verification, and coarse simple aperture photometry of
bright stars (\S~\ref{subsec:preparation}).  Using the information
collected from these initial steps, we select an astrometric reference
frame to which we transform all of the calibrated images. 
To construct a photometric reference frame,
we first convolve a subset of the frames to have identical stellar profiles,
and then stack them. Finally, we subtract each target frame
from the photometric reference frame (\S~\ref{subsec:imagesubtraction}).  We
perform aperture photometry on the subtracted images using positions
projected onto the frame from the Gaia-DR2 source catalog.  We detrend
the resulting light curves (\S~\ref{subsec:lcdetrending}).  The
resulting white noise and red noise properties of the light curves,
and a few interesting cases of variability, are discussed in
\S~\ref{sec:results}.

@@

The TESS spacecraft began science operations on July 25, 2018.  To
keep its cameras pointed opposite the Sun, the spacecraft advances by
$\approx$$28$ degrees east in ecliptic longitude every lunar month.
Data acquired throughout each one-month ``sector'' are downlinked at spacecraft
perigee through the Deep Space Network.  Descriptions of the
spacecraft's design and operations are given by
\citet{ricker_transiting_2015} and
\citet{vanderspek_2018}.

For us, the main data product of interest is the calibrated full frame
image (FFI).  Each TESS camera is read out every 2 seconds.  
The resulting pixel values are
averaged by the onboard computer into 30 minute exposures. An on-board
cosmic ray mitigation algorithm is applied \citep[][\S
5.1]{vanderspek_2018}. Once transmitted to the ground, the raw images
are calibrated by the Science Processing Operations Center (SPOC).  The
calibration process includes an overscan, bias, and dark current
correction, and also divides out a flat field.  Details are discussed
by \citet{clarke_kepler_2017}, and the resulting science data products
are described by \citet{tess_data_product_description_2018}.

We perform our processing using the calibrated images, the
corresponding uncertainty images, and the associated headers.  The
spacecraft has four cameras, and each camera has four CCDs.  In the
following analysis, all image-level operations are performed on
individual CCD images, so that at any instant of time there are 16
images that require analysis.

Sectors 1--5 mainly covered portions of the sky away from
the galactic plane.  Consequently, fewer than 2\% of the CDIPS target stars
were observed in the first five TESS sectors.  Although a few
interesting clusters are present in these observations ({\it e.g.},
Blanco~1, NGC~2516, NGC~1901), for the present work we opted to focus
on Sectors 6 \& 7, for which there were more stars of interest.
These begin in Sector 6 (2018-12-12, spacecraft orbit \#19),
and conclude at the end of Sector 7
(2019-02-01, spacecraft orbit \#22).
Sectors 6 and 7 cover galactic longitudes from roughly 200$^\circ$ to 280$^\circ$, 
with coverage within $\pm 20^\circ$ of the galactic plane
(Figure~\ref{fig:cdips_targets_positions}).

@@

Before we can perform any kind of photometry, a few janitorial tasks
are required.
First, we convert the multi-extension calibrated FITS image from MAST
into a single-extension FITS image, and trim the image to remove virtual rows
and columns using the \texttt{SCIROWS}, \texttt{SCIROWE},
\texttt{SCCSA}, and \texttt{SCCED} header values.

In order to account for the background variations present in
some frames due to scattered light from the Earth and Moon
\citep[see][\S 7.3.1--7.3.4]{vanderspek_2018}, we determine and
subtract a model of the large-scale background.  We do this by temporarily
masking out pixels more than $2\sigma$ from the image median, and then
pass a $48\times48$ median box filter over each pixel in the image,
with reflective boundary conditions.  The resulting background
estimate has low-amplitude structure over spatial scales of a few
pixels. We then blur the model image with a gaussian kernel of size 48 pixels,
which produces a smooth
background estimate.  These steps also remove
low-level vignetting in the corners of many images, which
remains even after flat-fielding \citep[see][\S
7.3.5]{vanderspek_2018}.  
The results are shown in the upper four panels of Figures~\ref{fig:stages_good}
and~\ref{fig:stages_bad}.
Features with spatial scales smaller than $\approx$48 pixels remain, 
but large scale patterns of scattered light are removed.

@@

After subtracting the background, we mask out saturated pixels using a
fixed saturation level of $8\times10^4$ analog-to-digital units (ADU). This value was
chosen based on the onset of bleeding charge trails in the images, and
is slightly greater than the saturation level of $2\times10^5$
electrons, or about $4\times10^4\,{\rm ADU}$, reported by
\citet{vanderspek_2018}. 
As a consequence, we do not analyze stars brighter than $T\approx 6.5$.
As described by \citet{Pal_2009}, the pixel masks are metadata attached
to the image file, and are only applied to the pixel values during the specific
image processing steps in which they are necessary ({\it e.g.},
convolution). We also extend the masks beyond purely saturated pixels
to ``bloomed'' pixels horizontally and vertically adjacent to the
saturated pixels (see Figure~6 of \citealt{Pal_2009}).

Finally, for frames with the \texttt{DQUALITY} bit-flag corresponding
to the ``momentum dumps'' and ``coarse pointing modes'' described by
\citet{vanderspek_2018}, we omit the entire frame.  This removes on
average a few frames per sector, out of about one thousand. Through
visual inspection, we see that the stars on these frames are extremely
smeared, and are unlikely to produce useful science data.  In
addition, we use the sector-specific data release notes\footnote{\url{
  archive.stsci.edu/tess/tess_drn.html}} to identify further times
with anomalous spacecraft performance, which we omit from
consideration.  This included three days at the
beginning of Sector 6 dedicated to acquiring pixel response function
data. There were no additional gaps in Sector 7.
%For Sectors 1 through 5, these
%include coarse pointing windows from orbits 10, 13, 14, and an
%instrumetal anomaly window in orbit 15.
% For Sectors 6 through 8, these include three days at the beginning of
% Sector 6 dedicated to acquiring pixel response function data, and also
% about three days during Sector 8 lost to an instrument anomaly.

@@

First, we perform source extraction on the
thousand or so brightest, non-saturated stars in each image.  
This is done using a \texttt{fitsh} tool, \texttt{fistar}.
We derive centroid positions for the stars, and
simultaneously
fit elliptical gaussians to their profiles, yielding the shape
parameters $(s,d,k)$, where the flux $f$ as a function of position
$(x,y)$ in the CCD image plane is assumed to take the form
\begin{align}
  f(x,y) &= B + A \exp \{ -0.5 \times [
    s(\Delta x^2 + \Delta y^2) + \\
    \nonumber
    &d(\Delta x^2 - \Delta y^2) +
    k(2\Delta x \Delta y)
  ]  \},
\end{align}
for $(x_0,y_0)$ the central coordinates of the star,
$\Delta x = x-x_0$, $\Delta y = y - y_0$, $B$ the background
level, and $A$ an arbitrary
flux-scaling constant.
For a nearly circular shape profile, the sharpness $s$ is related to
the FWHM as ${\rm FWHM} \approx 2.35\sqrt{s}$ \citep[{\it
e.g.},][]{Pal_2009}.  These shape parameters are later used when
selecting an astrometric reference frame
(\S~\ref{subsec:imagesubtraction}).  
In agreement with what is obvious upon visual inspection, this 
fitting process shows that stars closer to the
center of each camera's field are round, while
stars near the field edges are more triangular.

For the astrometric solution, we use the World Coordinate System (WCS)
and fourth-order Simple Imaging Polynomial (SIP) coefficients
derived by SPOC and included in the FFI headers
\citep[][Sec.~8]{pence_fits_2010}.  We explored the possibility of
using \texttt{astrometry.net} \citep{lang_2010} to derive our own
astrometric solutions for each frame, but found that the astrometric
residual (the mean separation between projected and measured
positions) was consistently a factor of 1.5-2 times higher in our WCS
solutions than in those given by SPOC.  This was perhaps because
we did not develop a robust
algorithm to select non-blended stars of intermediate brightness before
measuring their positions.
%Nonetheless, we did find that extending the astrometric correction
%to sixth order (compared to the fourth-order polynomial coefficients
%in the SPOC solution) did not improve the quality of the fit.

With the resulting WCS information, we then project a source catalog
onto each frame. 
We use the
projected positions of the sources to center the apertures in our
photometry,
rather than attempting to measure the positions.  Such
``forced-aperture photometry'' is preferable to source
extraction in the crowded fields that are central to this work.  The
Gaia-DR2 epoch is J2015.5, so even the fastest-moving stars with
proper motions of $\sim$$1\,{\rm arcsecond}\,{\rm yr}^{-1}$ are still
well within one pixel of their predicted positions in the TESS images.
The projection from catalog sky-coordinate positions to pixel
coordinates is performed using an analog of the \texttt{wcs-rd2xy}
program that performs the standard matrix algebra \citep{lang_2010}.
The source catalog look-up is performed using
\texttt{gaia2read}\footnote{\url{github.com/samuelyeewl/gaia2read}}
\citep{kim_2018_gaia2read}.

@@

Figure~\ref{fig:astromresid} displays the residual between
the measured and projected stellar centroid
positions for one photometric reference image.
The plot shows that the errors
are typically largest in the corners of the image,
where the non-linearity of the focal plane is most significant, and
the corrections required by the SIP coefficients are largest.
Also, the typical median precision of the WCS solution is a bit below
0.1 pixels, and its $90^{\rm th}$ percentile is typically less than
0.3 pixels.
In our reduction,
we therefore require
that each frame's median residual and 90th percentile remain
below 0.2 and 0.4
pixels, respectively. If this constraint is not met, the reduction fails.
This is an essential quality-control check for any forced-aperture
photometry pipeline.
%The distribution has a outlier tail of saturated stars which were
%masked, and thus do not have measureable centroid positions.
%The final sub-panel of Figure~\ref{fig:astrometricresidual} is a
%sanity check on the location of the projected positions, and also
%gives some context for our chosen aperture radii of 1, 1.5, and 2.25
%pixels.

Finally, to collect the metadata needed
to select photometric reference frames,
we perform
aperture photometry on the
bright stars.
This task is
performed by using \texttt{fiphot} to
sum the counts inside 
circular apertures centered on the projected stellar positions.
The pixel weights are equal to the fraction of the pixel
that falls within the circular aperture.  They are unity for pixels
entirely within the aperture, and fractional along the aperture
boundary. % (see \citealt{Pal_2009} Fig 17). 
The background levels are measured in annuli surrounding
the center of each aperture. 
%The raw flux of the object after background removal is then
%(\citealt{Pal_2009} Eq 65)
%\begin{equation}
%  f = \sum_{x,y} w_{x,y} (I_{x,y} - B) = f_{\rm total} - B r_0^2.
%  \label{eq:simple_aperture_phot}
%\end{equation}
%The resulting measurements, for instance of the background level of
%each aperture, and the number of stars with ``good'' photometry,
%can then be used to assess the photometric quality of each frame.

@@

The core operation of ``classical'' image subtraction is to
match a photometric reference image $R$ and a target image $I$ by computing
and applying a convolution kernel.  For ground-based data, this
``match'' typically corrects for differences in seeing or transparency
between the reference and target; for space-based data, the match
might correct for spacecraft jitter, or thermal and corresponding
point-spread function (PSF) variations.  The kernel, once applied to
the high signal-to noise reference, produces a model image, $M_{xy}$,
\begin{equation}
    M_{xy} = (R \otimes K)_{xy} + B_{xy},
    \label{eq:imagemodel}
\end{equation}
where $B_{xy}$ is a component of the model image that allows for
background variations, and $\otimes$ denotes convolution.  Since we
modeled the background separately (\S~\ref{subsec:preparation}), we
set $B_{xy}=0$.  The convolution kernel $K$ is typically decomposed
onto a basis,
\begin{equation}
K = \sum_i c_i K_i,
\end{equation}
where the coefficients $c_i$ are found by minimizing
\begin{equation}
    \chi^2 = \sum_{xy} \left( \frac{I_{xy} - M_{xy}}{\sigma_{xy}} \right)^2,
    \label{eq:chisq_conv}
\end{equation}
where $\sigma_{xy}$ is the uncertainty in the target image pixel
values.  Photometry is then performed on the difference image
$D_{xy}$, where $D_{xy} = I_{xy} - M_{xy}$.  For the present
reduction, the uncertainty in each target image pixel was taken to be
a constant.

@@

To make the above high-level picture work, we need to select
two ``reference frames'':
(1) the astrometric reference frame; and (2) the photometric reference frame.

To choose the astrometric reference frame, we search for frames with
large, round stars (big $s$, small $d$ and $k$ values).  We also
require that the frame have a low background level, as measured in
annuli around the bright stars selected in
\S~\ref{subsec:preparation}.  Finally, the astrometric reference
frame needs to have a large
number of detected sources (though the variance between TESS images was rather 
small).  We sort the image
using these metrics, and then select the astrometric reference frame from
successive intersections of each sorted list.

@@

The second required reference frame is the photometric reference frame,
which is used both to calculate the convolution kernel, and to obtain
a reference flux for each star.  To make it, we first choose 50 images
with low background measurements (measured for each frame from the
annuli around bright stars), and only consider frames with a
relatively large number of detected bright objects.  We then convolve
these candidate photometric reference frames to the frame with the
lowest background measurement, and construct the photometric
reference as the median image across the 50 frame stack.

Measuring the reference flux for each star is a non-trivial
operation.  First, we perform forced simple aperture photometry on the
photometric reference frame to measure the flux for each source.  The
local background is estimated in annuli, with neighboring stars masked
out during the background measurement.  If we were to stop
here, {\it it would be a mistake}.  The reference fluxes for faint
stars would be overestimated, due to crowding.  The relative amplitude
of photometric signals for faint stars would correspondingly be biased
to lower values.

To avoid this problem, after performing simple aperture photometry on
the reference frame, we fitted a line between the Gaia-DR2
magnitude of each star, and its measured flux.  The TESS $T$-band magnitude
was calculated according to Equation~1 of \citet{stassun_TIC8_2019}.
We then use the known catalog magnitude to predict the expected
reference flux for each star.  This accounts for crowding down to Gaia's
resolution limit of $\approx$1$''$, rather than the TESS limit of
$\approx$20$''$.

The final instrumental flux
values $f$ we report are given by \citep[][Equation~83]{Pal_2009} 
\begin{align}
f &=  f_{\rm reference} + f_{\rm subtracted} \\
&=
g \left(T_{\rm cat} \right)
+
\frac{1}{|| K ||_1^2} \sum_{x,y} D_{xy} (w \otimes K)_{xy}.
\label{eq:ism_flux_measurement}
\end{align}
The function $g$ takes as input the target star's catalog magnitude
$T_{\rm cat}$, and returns the reference flux.  Its coefficients are
found independently for each
aperture.  The difference image $D$ is equal to $I -  (R\otimes K)$,
where as in Equation~\ref{eq:imagemodel}, $I$ is the target image
transformed to the astrometric reference, $R$ is the photometric
reference, and $K$ is the convolution kernel.  The weights $w$ from
the circular aperture mask are included in the convolution.  The norm
$|| K ||_1$ is defined by \citet{Pal_2009}~Equation~81.

@@

To solve for the coefficients $c_i$ of the convolution kernel, a
few further assumptions are necessary.  The procedure implemented in
\texttt{ficonv} is to subdivide the image, and within each grid
element find the brightest non-saturated star. These isolated
``stamp'' stars are then used to solve for the coefficients of the
kernel, by minimizing Equation~\ref{eq:chisq_conv} over the sum of all
stamps.  For the kernel basis, we use a linear combination of
delta functions with a flux scaling term
(\citealt{soares-furtado_image_2017} Section 3.3.1 gives the
equations).  In this model, spatial variations of the PSF across the
image are captured by weighting each basis component with spatial
polynomials up to a cut-off order.
